---
title: "Local bodies extended"
author: ""
date: "2020-11-09"
params:
  orig_date: "Original Publish Date: 11 September, 2020"
  update_date: !r paste("Updated on:", format(Sys.time(), '%d %B, %Y'))
output:
  blogdown::html_page:
    toc: true
editor_options: 
  chunk_output_type: inline
---

---

### Document History

`r params$orig_date`

`r params$update_date`

---

```{r set up, warning=FALSE, include=FALSE, message= FALSE}

knitr::opts_chunk$set(cache = FALSE,echo = FALSE, message=FALSE, warning = FALSE,fig.width = 16/2, fig.height = 9/2)


library(tidyverse)
library(data.table)
library(knitr)
library(kableExtra)
library(scales)
library(gridExtra)
library(stargazer)
library(ggbump)
`%!in%` = Negate(`%in%`)

select <- dplyr::select
```

In this post we will be looking at dynasticism at the local level. We will be using two different definitions. 1 - category 2 - Where we only consider if an individual/set of individuals have connections to the ae-ge level. 2 - category 4 - We consider them as a dynast as long as they have/ have had members at one of the levels.



```{r}

dyn_all <-  read.csv("D:/cpr/up-dynasties/dyn_other_data/dyn_all.csv")

dyn_lb <- dyn_all %>% filter(election_type %!in% c("AE", "GE") & year >2001)



dyn_ulb <- dyn_lb %>% filter(election_type %in% c("NP", "NPP", "NN"))

dyn_nn <- dyn_lb %>% filter(election_type == "NN")

dyn_np <- dyn_lb %>% filter(election_type == "NP")

dyn_npp <- dyn_lb %>% filter(election_type == "NPP")

dyn_bp <- dyn_lb %>% filter(election_type == "BP")

dyn_zp <- dyn_lb %>% filter(election_type == "ZP")

dyn_rlb <- dyn_lb %>% filter(election_type %in% c("BP","ZP"))



```



**Category 4**

level                 Proportion of dynasts
----------------     ------------------
All LB                  `r data.frame(round(prop.table(table(dyn_lb$dyn_cum_4)),2))[2,2]`
ULB                     `r data.frame(round(prop.table(table(dyn_ulb$dyn_cum_4)),2))[2,2]`
RLB                     `r data.frame(round(prop.table(table(dyn_rlb$dyn_cum_4)),2))[2,2]`
NN                      `r data.frame(round(prop.table(table(dyn_nn$dyn_cum_4)),2))[2,2]`
NP                      `r data.frame(round(prop.table(table(dyn_np$dyn_cum_4)),2))[2,2]`
NPP                     `r data.frame(round(prop.table(table(dyn_npp$dyn_cum_4)),2))[2,2] `
BP                      `r data.frame(round(prop.table(table(dyn_bp$dyn_cum_4)),2))[2,2]`
ZP                      `r data.frame(round(prop.table(table(dyn_zp$dyn_cum_4)),2))[2,2]`


```{r}

## extending the second category to local body

##dyn_all %>% group_by(family_id)







```



